The difference operation between templates of binary cellular automata

### 2015-12-29 article/article.tex
Versão Final

It is noteworthy that the difference operation can generate a large number of templates, which may, in specific cases, not effectively reduce the search space. This is the principal drawbacks today, but the approach is relevant in general terms, and so more effective the greater the complexity of the attributes specified in the rules, i.e., the greater the number of properties that the rule space in question should either present or not. Although the work in \cite{deOliveira2014,deOliveira2014b} made it possible to specify templates of desired properties, the present work makes it possible to find templates that exclude unwanted properties.

Currently, the difference operation works with binary CAs, but its generalisation to higher values of $k$ is underway. The use of methods to treat templates as boolean algebraic expressions and so simplify them are also underway to help to reduce the search space, since this reduce is the main contribution of the difference operation between templates of binary cellular automata.

>>>>

It is noteworthy that the difference operation can generate a large number of templates, which may, in specific cases, not effectively reduce the search space. This is an issue we are currently addressing, by means of a technique for handling binary templates as Boolean algebraic expressions; initial experiments have clearly shown the effectiveness of the approach. Furthermore, since the difference operation is presently constrained for binary CAs, its generalisation to higher values of $k$ is also under way.

### 2015-12-29 manuscript/article.tex
Versão Final

It is noteworthy that the difference operation can generate a large number of templates, which may, in specific cases, not effectively reduce the search space. But the approach is relevant in general terms, and so more effective the greater the complexity of the attributes specified in the rules, i.e., the greater the number of properties that the rule space in question should either present or not. Although the work in \cite{deOliveira2014,deOliveira2014b} made it possible to specify templates of desired properties, the present work makes it possible to find templates that exclude unwanted properties.

Currently, the difference operation works with binary CAs, but its generalisation to higher values of $k$ is underway.

>>>>

It is noteworthy that the difference operation can generate a large number of templates, which may, in specific cases, not effectively reduce the search space. This is an issue we are currently addressing, by means of a technique for handling binary templates as Boolean algebraic expressions; initial experiments have clearly shown the effectiveness of the approach. Furthermore, since the difference operation is presently constrained for binary CAs, its generalisation to higher values of $k$ is also under way.
